\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
\thispagestyle{plain}
\setcounter{page}{3}
There are many people giving assistance on my thesis work. I am very grateful to each of them.
Most of all, I would like to show my deepest gratitude to my advisor, Prof. Che-Rung Lee.
Prof. Lee teaches me how to define problems, map out schedule of validation, analyse the result of experiments and do great presentation.
While discussing problems with Prof. Lee, I learned to use mathematical method to solve problems and proofed the results. In addition, Prof. Lee always helps me find the right direction to overcome difficulties. Therefore, I got more progress in study and also be more delighted on doing research.
Except researching, Prof. Lee provided me the chance to train the junior students to attend Student Cluster Competition. I learned a lot and been inspired while I was teaching and discussing with them.

I would like to express thanks to Dr. I-Hsin Chung, a cooperative partner in IBM, he gave me advises on project and help me learn professional knowledge about my research. Except working, Dr. Chung also teached me the importance of relationship and provided me a chance to get a job in IBM.
And My lab mates also support me on my way of research during the two years. They gave me favors anytime I needed helps. I really appreciate scope lab.

My family always encourage me to achieve my best. I am very grateful to my parents and my brother.
Thanks to all the people around me.

\end{abstract} 